Tabular Constraint Learning

### 2016-04-12 Paper/ECAI/tabular.tex
implemenation note

>>>>

\paragraph{Implementation note} Essentially for each constraint both \generategroups and \findassignment are separate constraint satisfaction problems. Hence, it is natural to solve them using declarative solvers. Even though each is a separate constraint problem, they are variations of each other and can be modeled using similar techniques. It also makes an extension of the system easy, we can solve new variations by adding, removing or modifying constraints from a similar constraint satisfaction problem. Furthermore, the declarative languages such as ASP \cite{whaisasp} and Minizinc \cite{minizinc} provide primitives that make modeling transparent and generic.

Our system internally supports ASP (using Clingo 4.5.4 \cite{clingo}), Minizinc (Gecode-backend 2.0.2 \cite{minizinc}) and a native python CSP solver \cite{python_constraint}. All the constraints mentored in the paper can be run purely in the internal python engine without any external software. The future versions of the system will provide user interfaces to the ASP, Minizinc and Python-Constraint languages.
